What is disputed on the web?

### 2010-01-26 papers/wicow_claimfinder/claimfinder.tex
Python noun extraction. Added a table of claim phrases to the paper

@@

@@

@@

>>>>

Not everything on the Web is accurate or unbiased. One way to determine that information on the web should not be trusted is if a trustworthy source elsewhere on the web is explicitly disagreeing

We describe a method for the automatic acquisition of a database of

We describe a method for automatically aquiring a collection of claims that

@@

\begin{figure}[tb]
  \begin{tabular}{|ll|}
    \hline
    {\bf Google Count} & {\bf Template}\\ 
    \hline
    \multicolumn{2}{|c|}{\it Something that could be challenged}\\
    163,000,000 & believe that \\
    206,000,000 & think that \\
    49,500,000 & idea that \\
    33,600,000 & claim that \\
    \hline
    \multicolumn{2}{|c|}{\it Something others believe}\\
    120,000,000 & the belief that \\
    49,000,000 & who believe that \\
    50,500,000 & who think that \\
    10,100,000 & believing that \\
    9,430,000 & claiming that \\
    \hline
    \multicolumn{2}{|c|}{\it Something false}\\
    9,960,000 & into believing that \\
    15,600,000 & the misconception that \\
    13,000,000 & the delusion that \\
    12,400,000 & the myth that \\
    7,190,000 & the mistaken belief that \\
    4,950,000 & the fallacy that \\
    3,720,000 & the lie that \\
    3,600,000 & the false belief that \\
    2,140,000 & the deception that \\
    1,760,000 & the misunderstanding that \\
    148,000 & false claim that \\
    1,090,000 & false claim is that \\
    1,630,000 & mistakenly believe that \\
    3,700,000 & mistaken belief that \\
    530,000 & the absurd idea that \\
    1,290,000 & the hoax that \\
    3,440,000 & the deceit that \\
    681,000 & falsely claimed that \\
    103,000 & falsely claiming that \\
    373,000 & erroneously believe that \\
    140,000 & erroneous belief that \\
    334,000 & the fabrication that \\
    72,600 & falsely claim that \\
    152,000 & bogus claim that \\
    65,300 & urban myth that \\
    654,000 & urban legend that \\
    224,000 & the fantasy that \\
    171,000 & incorrectly claim that \\
    249,000 & incorrectly claimed that \\
    232,000 & incorrectly believe that \\
    98,900 & stupidly believe that \\
    429,000 & falsely believe that \\
    376,000 & wrongly believe that \\
    189,000 & falsely suggests that \\
    280,000 & falsely claims that \\
    59,500 & falsely stated that \\
    698,000 & absurdity of the claim that \\
    136,000 & no longer believe that \\
    659,000 & no longer think that \\
    \hline
  \end{tabular}

\end{figure}

\x{Some prefixes suggest that some disagree, without saying that they do. E.g. ``people who believe that''}

@@

\x{Remove anything containing stuff like 'if'}
\x{Disallow possesives like its/his etc unless a noun has come first}
\x{Strip HTML tags}

@@

\x{Named entity recognition}
